Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-06-27 WRITEUP/ms.tex
few details about some figures; comparison with grisdale added

Based on Equation~\ref{eqn:SVE}, a one-to-one mapping between $\sigma_{\rm gas}^2/R$ and $\Sigma$ is therefore expected for a virialized cloud, since $\sigma_{\rm gas}^2/R\propto\Sigma$. Deviations from this relation are usually attributed to a significant contribution from external pressure as per Equation~\ref{eqn:v0} (see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}).

Summarizing, the virial parameter can be used to quantify the stability/boundedness of
%mm an MCC.
    a molecular cloud.
Accounting for the external pressure, a virial parameter of $\alpha_{\rm vir}\lesssim2$ would be unstable \citep{Bertoldi92b}.
%
Such a criterion is often used in \obs \citep[see e.g., ][]{Kauffmann17b}.

@@

\begin{figure*}[htbp]
 \centering
  \includegraphics[width=\textwidth, trim=25 25 35 30, clip]{\figpath/SS_bigfonts/{combined}.pdf}
\caption{
Examples of MCCs (white contours) identified by the clump finder in
\flower during its accreting phase (\Fig{SFH}a; left two columns), where \flower display a highly disturbed gas morphology, and 
its quiescent phase (right two columns), where \flower shows a rotating disk configuration.
Panels in the second and fourth columns show the molecular gas distribution projected along different viewing angles. 
Colorbar on the right shows the mean H$_2$ number density, weighted by gas mass. 
Different rows show the results obtained by applying different H$_2$ number density cuts $(n_{\rm cut})$ as annotated by the label in the bottom left corners. 
\label{fig:MCC}
}
\end{figure*}

@@

\subsection{Distributions of MCC Basic Properties and Outlier} \label{sec:dist}
\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/minmaxNcut_basicDistributions.pdf}
\caption{Normalized distributions of mass (left), size (middle), and gas mass fraction (right) of MCCs identified using the lowest 
$n_{\rm cut}$\eq0.32\,\cc (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels) over all the considered evolutionary stages of \flower traced in the simulation. Note that the scales shown on the $y$-axes are different between the top and bottom panels, as fewer MCCs are identified at higher $n_{\rm cut}$.
\label{fig:dist}}
\end{figure*}

@@

The most massive structures ($M_{\rm gas}>$10$^7$\,\Msun) correspond to the molecular disk of the galaxy (see e.g., \Fig{MCC}), 
which is identified as a single component at low $n_{\rm cut}$. This main disk component occupy the top right corner of \Fig{stellarRatio16}, with a 
low gas mass fraction of $f_{\rm gas}\simeq$\,0.
The velocity dispersion of such structure is dominated by bulk motions, as shown in \Fig{vv}, where we compare 
the velocity dispersions of MCCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) 
in the accreting and quiescent phases of \flower.
The accreting phase of \flower displays a disturbed morphology, whereas the 
quiescent phase displays a disk-like morphology (\Fig{MCC}).
Excluding the structure corresponding to the molecular disk, the 
velocity dispersions of most MCCs in the accreting phase of \flower are dominated by turbulent motions.
On the other hand, $\sigma_{\rm bulk}$ is at least comparable to $\sigma_{\rm NT}$ for almost half the MCCs
in the quiescent disk-like phase.

The most massive MCC is excluded in the discussion of MCC dynamics in \Sec{diss} of this paper,
since its dynamics is dominated by large-scale shear; however, we include them in the scaling relation plots (\Fig{larsons_single} and \Fig{alpha16-28}) 
as would be done so for an observational study. % where we would plot everything we identify and try to interpret their nature.

Considering only the MCCs identified at the highest density threshold, the mass of MCCs is $\simeq10^{6.5}$\,\Msun.
We note that similarly massive molecular structures (few times 10$^7$\,\Msun\footnote{See \S{3.1} of \citet{Behrendt16a}.}) 
have been reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., a maximum resolution of 3\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}). However, the stellar feedback, IGM, merger and accretion histories are not properly modeled in such simulations. That said, the similar mass range found in MCCs of \flower\ is reassuring --- our results are not far off in spite of the limited resolution ($l_{\rm cell}\simeq$\,30\,pc).

@@

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/3by2_clumpProp_ss16-ss22.png}
\caption{
Linewidth-size relation (top), $\alpha_{\rm vir}$-mass relation
(middle), and $\sigma_{\rm gas}^2/R$-$\Sigma_{\rm gas}$ relation (bottom) for
MCCs (star symbols) identified in the two most extreme evolutionary
stages of \flower\ --- accreting (left) and starburst (right). Star symbols are color-coded by density thresholds
$n_{\rm cut}$, as illustrated by the colorbar shown on the right.
Gas-only $\alpha_{\rm vir}$ (orange star symbols) is overplotted, and is of the same order of magnitude as $\alpha_{\rm vir, tot}$ for most MCCs
since they are gas-dominated (see \Fig{stellarRatio16}). 
Stability of the biggest structures is strongly influenced by the stellar component, given their low $f_{\rm gas}$ (see \Fig{stellarRatio16} and \Sec{dist}).
The gray dotted lines shown in the bottom panels correspond to the various annotated external pressures needed in order for
the gas to be in equilibrium, see Equation~\ref{eqn:v0}.
Literature data are taken from \citet{Larson81a, Heyer04a, Rosolowsky05a, Bolatto08a, 
Swinbank11a, Leroy15a, Kauffmann17a}, % black dot = extragalactic GMCs in quiescent environments
MCCs in the starburst phrase have lower $\alpha_{\rm vir}$ than in the accreting phase.
and \citet{Kauffmann17b}.
\label{fig:larsons_single}}
\end{figure*}

>>>>

Based on Equation~\ref{eqn:SVE}, a one-to-one mapping between $\sigma_{\rm gas}^2/R$ and $\Sigma$ is therefore expected for a virialized cloud, since $\sigma_{\rm gas}^2/R\propto\Sigma$. Deviations from this relation are usually attributed to a significant contribution from external pressure as per Equation~\ref{eqn:v0} (see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}). Similar conclusions are also reached from the analysis of clouds forming in Milky-Way like galaxy simulated with a $\simeq 4\,{\rm pc}$ resolution \citep[i.e.][]{grisdale:2018}.

Summarizing, the virial parameter can be used to quantify the stability/boundedness of a molecular cloud. Accounting for the external pressure, a virial parameter of $\alpha_{\rm vir}\lesssim2$ would be unstable \citep{Bertoldi92b}. Such a criterion is often used in \obs \citep[see e.g., ][]{Kauffmann17b}.

@@

\begin{figure*}[htbp]
 \centering
  \includegraphics[width=\textwidth, trim=25 25 35 30, clip]{\figpath/SS_bigfonts/{combined}.pdf}
\caption{
Examples of MCCs identified in \flower by our clump finder.
%
The identified structures (white contour) are superimposed on the map of the mass weighted $H_2$ density field of the galaxy.
%
Two stages of \flower are selected: the accreting phase (left two columns, see \Fig{SFH}a for the definition) and the quiescent phase (right two columns), where \flower display a highly disturbed gas morphology, and a rotating disk configuration, respectively.
%
Panels in the second and fourth columns show the molecular gas distribution projected along different viewing angles. 
%
Different rows show the results obtained by applying different H$_2$ number density cuts $(n_{\rm cut})$, as annotated in each panel. \AP{please change $\rm Kpc$ to $\rm kpc$}
\label{fig:MCC}
}
\end{figure*}

@@

\subsection{Distributions of MCC Basic Properties and Outlier} \label{sec:dist}
\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/minmaxNcut_basicDistributions.pdf}
\caption{Normalized distributions of mass (left), size (middle), and gas mass fraction (right) of MCCs identified using the lowest 
$n_{\rm cut}$\eq0.32\,\cc (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels) over all the considered evolutionary stages of \flower traced in the simulation. Note that the scales shown on the $y$-axes are different between the top and bottom panels, as fewer MCCs are identified at higher $n_{\rm cut}$. \AP{please change $M_{\rm cl}$ into $M_{\rm gas}$}
\label{fig:dist}}
\end{figure*}

@@

The most massive structures ($M_{\rm gas}>$10$^7$\,\Msun) correspond to the molecular disk of the galaxy (see e.g., \Fig{MCC}), which is identified as a single component at low $n_{\rm cut}$. This main disk component occupy the top right corner of \Fig{stellarRatio16}, with a low gas mass fraction of $f_{\rm gas}< 5\%$. The velocity dispersion of such structure is dominated by bulk motions, as shown in \Fig{vv}, where we compare the velocity dispersions of MCCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) in the accreting and quiescent phases of \flower. The accreting phase of \flower displays a disturbed morphology, whereas the quiescent phase displays a disk-like morphology (\Fig{MCC}).
%
Excluding the structure corresponding to the molecular disk, the velocity dispersions of most MCCs in the accreting phase of \flower are dominated by turbulent motions. On the other hand, $\sigma_{\rm bulk}$ is at least comparable to $\sigma_{\rm NT}$ for almost half the MCCs in the quiescent disk-like phase.
%
For these reasons, the most massive MCCs are excluded in the discussion of the dynamics (\Sec{diss}), as they are dominated by large-scale shear; however, we include them in the scaling relation plots (\Fig{larsons_single} and \Fig{alpha16-28}), as would be done so for an observational study.

Considering only the MCCs identified at the highest density threshold, the mass of MCCs is $\simeq10^{6.5}$\,\Msun. We note that similarly massive molecular structures (few times 10$^7$\,\Msun\footnote{See \S{3.1} of \citet{Behrendt16a}.}) have been reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., a maximum resolution of 3\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}). However, the stellar feedback, IGM, merger and accretion histories are not properly modeled in such simulations, e.g. see \citet{grisdale:2017,grisdale:2019} for the importance of feedback in shaping the properties of clouds forming in local simulated galaxies. That said, the similar mass range found in MCCs of \flower\ is reassuring --- our results are not far off in spite of the limited resolution ($l_{\rm cell}\simeq$\,30\,pc).

@@

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/3by2_clumpProp_ss16-ss22.png}
\caption{
Linewidth-size relation (top), $\alpha_{\rm vir}$-mass relation
(middle), and $\sigma_{\rm gas}^2/R$-$\Sigma_{\rm gas}$ relation (bottom) for
MCCs (star symbols) identified in the two most extreme evolutionary
stages of \flower\ --- accreting (left) and starburst (right). Star symbols are color-coded by density thresholds
$n_{\rm cut}$, as illustrated by the colorbar shown on the right.
Gas-only $\alpha_{\rm vir}$ (orange star symbols) is overplotted, and is of the same order of magnitude as $\alpha_{\rm vir, tot}$ for most MCCs
since they are gas-dominated (see \Fig{stellarRatio16}) \AP{I think the orange points makes the figure more messy, an alternative would to remove them and discuss the point in the text}. 
Stability of the biggest structures is strongly influenced by the stellar component, given their low $f_{\rm gas}$ (see \Fig{stellarRatio16} and \Sec{dist}).
The gray dotted lines shown in the bottom panels correspond to the various annotated external pressures needed in order for
the gas to be in equilibrium, see Equation~\ref{eqn:v0}.
Literature data are taken from \citet{Larson81a, Heyer04a, Rosolowsky05a, Bolatto08a, 
Swinbank11a, Leroy15a, Kauffmann17a}, % black dot = extragalactic GMCs in quiescent environments
MCCs in the starburst phrase have lower $\alpha_{\rm vir}$ than in the accreting phase.
and \citet{Kauffmann17b}.
\label{fig:larsons_single}}
\end{figure*}
